Bayesian Inference from Time Series: Information Loss and the Whittle Likelihood

### 2018-03-07 doc/ms.tex
Nonzero frequencies

The whittle likelihood is
\begin{align}
p(\boldsymbol{y} | \boldsymbol{\theta})
    &\propto \exp\left(-\sum_{k=1}^{\lfloor N/2 - 1 \rfloor}
         \left[S(\omega_k; \boldsymbol{\theta})
         + \frac{I(\omega_k; \boldsymbol{y})}
                {S(\omega_k; \boldsymbol{\theta})}\right]
                \right)
\label{eqn:whittle}
\end{align}
where $I(\omega_k; \boldsymbol{y})$ is the power spectrum of the data,
$S(\omega_k; \boldsymbol{\theta})$ is the power spectral density implied
by the model parameters, and the summation is over the angular frequencies
involved in the first half of the discrete fourier transform.
Equation~\ref{eqn:whittle} is equivalent to an exponential distribution
for the empirical power spectrum (i.e., the periodogram)
$I(\omega_k; \boldsymbol{y})$ whose expectation is given by the
model power spectrum (i.e., the power spectral density)
$S(\omega_k; \boldsymbol{\theta})$.

>>>>

The whittle likelihood is
\begin{align}
p(\boldsymbol{y} | \boldsymbol{\theta})
    &\propto \exp\left(-\sum_{k=1}^{\lfloor N/2 - 1 \rfloor}
         \left[S(\omega_k; \boldsymbol{\theta})
         + \frac{I(\omega_k; \boldsymbol{y})}
                {S(\omega_k; \boldsymbol{\theta})}\right]
                \right)
\label{eqn:whittle}
\end{align}
where $I(\omega_k; \boldsymbol{y})$ is the power spectrum of the data,
$S(\omega_k; \boldsymbol{\theta})$ is the power spectral density implied
by the model parameters, and the summation is over the nonzero angular frequencies
involved in the first half of the discrete fourier transform.
Equation~\ref{eqn:whittle} is equivalent to an exponential distribution
for the empirical power spectrum (i.e., the periodogram)
$I(\omega_k; \boldsymbol{y})$ whose expectation is given by the
model power spectrum (i.e., the power spectral density)
$S(\omega_k; \boldsymbol{\theta})$.
